### 2023-06-23 manuscript.tex
cite Van de Sompel 2015 for signposting [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/196b2c0a09b766bbcc026f7504f34a805280a9fc.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/196b2c0a09b766bbcc026f7504f34a805280a9fc/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5357287070

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/18c218220087b13fe0db935b3c1a320647449330/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/18c218220087b13fe0db935b3c1a320647449330}{stain/2022-fdo-paper@18c2182}
on June 23, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/196b2c0a09b766bbcc026f7504f34a805280a9fc/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/196b2c0a09b766bbcc026f7504f34a805280a9fc}{stain/2022-fdo-paper@196b2c0}
on June 23, 2023.
